\documentclass[11pt]{article}
%\documentstyle{article}

% hyperref setup
\usepackage{amsmath}
\usepackage{epsfig,graphics}
\usepackage{etoolbox}
\usepackage{hyperref,url}
\hypersetup{colorlinks=true,urlcolor=blue,citecolor=Cerulean}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\makeatletter
\def\@footnotecolor{red}
\define@key{Hyp}{footnotecolor}{%
 \HyColor@HyperrefColor{#1}\@footnotecolor%
}
\patchcmd{\@footnotemark}{\hyper@linkstart{link}}{\hyper@linkstart{footnote}}{}{}
\makeatother
\hypersetup{footnotecolor=blue}




\usepackage{enumitem}
\setenumerate{leftmargin=*}


\renewcommand*\labelenumi{[\theenumi]}
\usepackage{geometry}
\geometry{letterpaper,left=1.22in,right=1.22in,top=1in,bottom=1in}

\pagestyle{empty}

\newcommand{\head}[1]{
  \vspace{10pt}
  {\Large \bf #1} \\*[-0.8pc]
  \underline{\hspace{6.07in}}}

\newcommand{\subhead}[1]{
  \vspace{10pt}
  {\large \textbf{#1}}}

\newcommand{\datedentry}[2]{
  \vspace{5pt}
  \begin{minipage}{5in}{\textbf{#1}}\end{minipage}
  \hfill
  \begin{minipage}{1in}{\hfill\textit{#2}}\end{minipage}
  %\vspace{5pt}
  }

  \newcommand{\ddatedentry}[2]{
 %   \vspace{2.7pt}
  %\begin{minipage}{5in}
  {#1}
  %\end{minipage}
  \hfill
  \begin{minipage}{.5in}{\hfill\textit{#2}}\end{minipage}
 % \vspace{7pt}
  }


\newcommand{\datedentryy}[2]{
  \begin{minipage}{5in}{\textbf{#1}}\end{minipage}
  \hfill
  \begin{minipage}{.5in}{\hfill\textit{#2}}\end{minipage}
 %\vspace{5pt}
 }

\newcommand{\undatedentry}[2]{
  \vspace{10pt}
  \textbf{#1}

  \vspace{5pt}}

\begin{document}

\begin{center}
  \begin{Large}
    \textbf{Ethan Berger Anderes} \\ \vspace{5pt}
  \end{Large}
  Curriculum Vitae\footnote{Suppporting documents, including publication preprints, can be found at \url{https://github.com/EthanAnderes/Curriculum-Vitae}}\\
  Department of Statistics\\
  University of California at Davis\\
  (773) 315-3613\\
  \texttt{anderes@ucdavis.edu}
\end{center}

\flushleft
\head{Education}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5


\datedentry{Ph.D. in Statistics, University of Chicago}{ 2005}\\
\vspace{5pt}
Thesis: %\textquotedblleft Estimating Deformations of Gaussian Random Fields.\textquotedblright
{\sl Estimating Deformations of Gaussian Random Fields.}

Adviser: {\sl Michael L. Stein.}

\vspace{2pt}

\datedentry{Bachelor of Arts in Mathematics, University of Minnesota }{2000}\\
\vspace{4pt}
\datedentry{Bachelor of Arts in Philosophy, University of Minnesota }{2000}

\head{Professional Experience}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5


\datedentry{Associate Professor, Department of Statistics\\
University of California at Davis}{2014-present}

\vspace{7pt}


\datedentry{Assistant Professor, Department of Statistics\\
University of California at Davis}{2008-2014}

\vspace{7pt}

\datedentry{Visiting Assistant Professor, Department of Statistics\\
University of California at Berkeley}{2006-2008}

\vspace{7pt}

\datedentry{NSF Mathematical Sciences Postdoctoral Fellowship\\
University of California at Berkeley}{2005-2008}

\vspace{7pt}

\datedentry{Research and Software Development \\
Jet Propulsion Laboratory, NASA}{Summer 2007}
%
%%\datedentry{Teaching Assistant, Department of Statistics,\\ University of Chicago}{2000-2005}
%
%% Statistics 381/383/385: {\it Measure Theoretic Probability}\\
% %Graduate level course for Ph.D. students.
% %\vspace{5pt}
%
% %Statistics 251: {\it Intro to Math Probability}\\
% %Undergraduate introductory course on probability.
% %\vspace{5pt}
%
% %Statistics 220e: {\it Statistical Methods and Their Application}\\
% %Undergraduate course on statistics with emphasis for economics majors.
%
%\datedentry{Instructor, Department of Statistics, \\
%University of Chicago and University of California at Berkeley}{2002,2005-2008}
%\vspace{1mm}
%{\it Spatial Statistics, 212A.} Fall 2007. \\
%Graduate course, UC Berkeley.
%
%\vspace{3mm}
%
%{\it Introduction to Probability and Statistics, 20.}   Fall and spring  2006.   \\
%Undergraduate course on statistics, UC Berkeley.
%
%
%\vspace{3mm}
%
%{\it Statistical methods and their application, 220e.} Winter 2002.   \\
%Undergraduate course on statistics for econ majors, University of Chicago.
%
%
%
%
%\datedentry{Consultant, Department of Statistics, University of Chicago}{2000-2005}
%
%\begin{minipage}{6in}
% Advised university researchers from the departments of Ecology and Evolution, Neurobiology, Medicine,
%and Political Science.
%\end{minipage}


%\vspace{7pt}
\head{Current Preprints}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{.1mm}


\begin{enumerate}[labelindent=0pt]


\item
E. Anderes, S. Borgwardt and J. Miller. \textsl{Discrete Wasserstein Barycenters: Optimal Transport for Discrete Data}.
\url{http://arxiv.org/abs/1507.07218}.



\item
E. Anderes and M. Coram.  \textsl{A general spline representation for nonparametric and semiparametric density estimates using diffeomorphisms.}  \url{arxiv.org/abs/1205.5314}.

\end{enumerate}



\newpage


%\vspace{7pt}
\head{Published Papers}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \vspace{.1mm}



\begin{enumerate}[labelindent=0pt]


\item
E. Anderes, B. D. Wandelt and G. Lavaux (2014). \textsl{Bayesian inference of CMB gravitational lensing.} \textit{The Astrophysical Journal} {\bf 808}, 152




\item
E. Anderes (2013).
\textsl{Decomposing CMB lensing power with simulation.} \\
\textit{Physical Review D} {\bf 88}, 083517


\item
E. Anderes, Huser, R., Nychka, D., Coram, M. (2013). \textsl{Nonstationary positive definite tapering on the plane.}  \textit{Journal of Computational and Graphical Statistics} {\bf 22}, 4, 848-865.



\item
E. Anderes and D. Paul (2012).  \textsl{Shrinking the quadratic estimator of weak lensing.}
\textit{Physical Review D} {\bf 85}, 103003.



\item
E. Anderes and A. van Engelen (2012). \textsl{The matter spectral density from lensed CMB observations.
.} \textit{Statistical Challenges in Modern Astronomy V}, Springer-Verlag, New York.


\item
E. Anderes (2012).  \textsl{Robust Adaptive Wiener Filtering.}  Refereed paper for \textit{IEEE International conference on image processing}.


\item
E. Anderes (2012). \textsl{Kriging.}  \textit{Encyclopedia of Environmetrics ed2}, Wiley.




\item
E. Anderes, L. Knox, A. van Engelen (2011).  \textsl{Mapping gravitational lensing of the CMB using local likelihoods.}
\textit{Physical Review D} {\bf 83}, 043523.



\item
E. Anderes and M. Stein (2011).  \textsl{Local likelihood estimation for nonstationary random fields.}  \textit{Journal of Multivariate Analysis} {\bf 102}, 506-520.




\item
E. Anderes and M. Coram (2011).   \textsl{Two dimensional density estimation using smooth invertible transformations.}
 \textit{Journal of Statistical Planning and Inference} {\bf 141}, 1183-1193.



\item
E. Anderes (2010).  \textsl{On the consistent separation of scale and variance for gaussian random fields.} \textit{The Annals of Statistics} {\bf 38}, 870-893.



\item
E. Anderes, B. Yu, V. Jovanovic, C. Moroney, M. Garay, A. Braverman, E. Clothiaux (2009).
\textsl{Maximum likelihood estimation of cloud height from multi-angle satellite imagery.}   \textit{Annals of Applied Statistics} {\bf 3}, 902-921.


\item
E. Anderes and S. Chatterjee (2009). \textsl{Consistent estimates of deformed isotropic gaussian random fields on the plane.} \textit{The Annals of Statistics} {\bf 37}, 2324-2350.



\item
E. Anderes and M. Stein. (2008). \textsl{Estimating deformations of isotropic gaussian random fields on the plane.} \textit{The Annals of Statistics} {\bf 36}, 719-741.


 \end{enumerate}

\newpage

%
%\head{Five most recent presentations} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

%\vspace{5pt}
\head{Grants}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 \vspace{.1mm}


\datedentry{NSF CAREER grant DMS-1252795}{2013-present}\\
Title: {\sl Deformations in statistics, cosmology and image analysis.}

\vspace{7pt}

\datedentry{NSF grant DMS-1007480 }{2009-2014}\\
Title: {\sl Local Likelihood Estimation for Nonstationary Random Fields.}

\vspace{9pt}

\datedentry{NSF Mathematical Sciences Postdoctoral Fellowship}{2005-2008}
University of California at Berkeley



\vspace{5pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\head{Professional Service}


\datedentry{Treasurer}{2015}
Nonparametric Section of the American Statistical Association

\vspace{7pt}

\datedentry{NSF panel reviewer}{2015}
Division of Mathematical Sciences

\vspace{7pt}


\datedentry{Co-organizer}{2014}
UC Davis Statistical Sciences Symposium on \\
Spatial-Temporal Statistics: Methods and Applications, UC Davis

\vspace{7pt}

\datedentry{Associate Editor}{2013 - 2014}
The American Statistician

\vspace{7pt}

\datedentry{President}{2011}
Sacramento branch of the ASA

\vspace{7pt}

\datedentry{Vice President}{2010}
Sacramento branch of the ASA

\vspace{7pt}

\datedentry{Co-organizer}{2011}
UC Davis Statistical Sciences Symposium on \\
Statistical Methods for Astronomy and Astrophysics, UC Davis

\vspace{7pt}

\datedentry{Member}{2008 - present}
Universe at UCDavis Initiative


\vspace{5pt}
%%%%%%%%%%%%%%%%%%%%%%
\head{Invited Lectures}
%\vspace{.001mm}


\begin{enumerate}


\item
\ddatedentry{Invited presentation, ICSA Graybill Conference, Fort Collins, CO.}{2015}


\item
\ddatedentry{Invited presentation, IMS-China International Conference, Kunming, China.}{2015}

\item
\ddatedentry{Invited presentation, Computing the Universe workshop, Berkeley, CA.}{2015}

\item
\ddatedentry{Invited presentation, IMS Asia Pacific Rim Meeting, Taipei, Taiwan.}{2014}


\item
\ddatedentry{Invited presentation,  Carnegie Mellon University, Pittsburgh, PA.}{2014}


\item
\ddatedentry{Invited presentation,  Joint Statistical Meeting, Boston, MA.}{2014}


\item
\ddatedentry{Invited presentation, ICSA International Conference, Hong Kong, China.}{2013}

\item
\ddatedentry{Invited presentation, BIRS CosmoStat13 workshop, Banff, Canada.}{2013}

\item
\ddatedentry{Invited seminar, Columbia University,  NY.}{2013}


\item
\ddatedentry{Invited seminar, University of Michigan, Ann Arbor, MI.}{2013}


\item
\ddatedentry{Invited seminar, Stanford University.}{2012}

%\ddatedentry{Invited talk  at IEEE International conference on image processing, FL.}{2013}

\item
\ddatedentry{Invited presentation, Workshop on Computer Science and
Statistics of \\Contemporary CMB data analysis, Paris, France.}{2012}

\item
\ddatedentry{Topic contributed paper and talk, Joint Statistical Meeting, San Diego, CA.}{2012}

\item
\ddatedentry{IMS invited session, IMS Asia Pacific Rim meeting, Tsukuba, Japan.}{2012}


\item
\ddatedentry{IMS invited session WNAR Annual Meeting, Fort Collins, Colorado.}{2012}

\item
\ddatedentry{Invited seminar, Center for Time Domain Informatics, \\ University of California at Berkeley.}{2012}

\item
\ddatedentry{Invited seminar, University of Rome, Tor Vergata, IT.}{2012}

\item
\ddatedentry{Invited presentation, Workshop on Statistical Methods for \\
Astronomy and Astrophysics, UC Davis.}{2011}


\item
\ddatedentry{Invited presentation, Conference on Statistical Challenges in \\ Modern Cosmology V, Penn State.}{2011}


\item
\ddatedentry{Invited seminar, University of California at Davis.}{2011}

\item
\ddatedentry{Topic contributed paper and talk, Joint Statistical Meeting, Vancouver, BC.}{2010}

\item
\ddatedentry{Invited presentation, Interface Conference, Seattle.}{2010}


\item
\ddatedentry{Invited presentation, Conference on the Frontiers of Statistical Decision Making\\ and  Bayesian Analysis in Honor of James O. Berger, San Antonio.}{2010}


\item
\ddatedentry{Invited new-researcher presentation, SAMSI conference, Space-time Analysis for  \\ Environmental Mapping, Epidemiology and Climate Change. SAMSI.}{2009}

\item
\ddatedentry{Invited presentation, Oberwolfach conference, Challenges in Statistical Theory: \\Complex Data Structures and Algorithmic Optimization, Germany.}{2009}


\item
\ddatedentry{Invited seminar, University of California at Riverside.}{2009}

\item
\ddatedentry{Invited presentation, Stanford Institute for Theoretical Economics.}{2008}


\item
\ddatedentry{Invited  presentation, International Biometric Society, ENAR, Arlington.}{2008}

\item
\ddatedentry{Invited presentation, Data Users Science Symposium, Caltech, Pasadena.}{2006}

\item
\ddatedentry{Invited presentation, International Biometric Society, ENAR meeting, Tampa.}{2006}


\end{enumerate}

%\datedentry{Ella Thorp Math Undergraduate Scholarship,\\
%University of Minnesota}{1998-2000}
%\datedentry{Ian Richards Math Undergraduate Scholarship,\\
%University of Minnesota}{1998-1999}
%\datedentry{Math Undergraduate Scholarship,\\
%University of Minnesota}{1999-2000}
%\datedentry{NSF Undergraduate Research Experiences, \\
%University of Minnesota}{1999-2000}

%\head{Computer Skills}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{10pt}
%Proficient in \textsc{Matlab}. Extensive experience with C, \textsc{Mathematica}, R, and \LaTeX.
%

%
%\head{References}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{10pt}
%\begin{tabular}{ll}
%\begin{tabular}{l}
%{\bf Professor Bin Yu}\\
%Department of Statistics\\
%University of California at Berkeley\\
%email: \texttt{binyu@stat.berkeley.edu}\\
%phone: (510) 642-2021
%\end{tabular}
%&
%\begin{tabular}{l}
%{\bf Professor Michael Stein}\\
%Department of Statistics\\
%University of Chicago\\
%email: \texttt{stein@galton.uchicago.edu}\\
%phone: (773) 702-8326
%\end{tabular}
%\\
%{}&{}\\
%\begin{tabular}{l}
%{\bf Professor Marc Coram}\\
%Department of Health Research and Policy\\
%Stanford University School of Medicine\\
%email: \texttt{mcoram@stanford.edu}\\
%phone: (650) 723-9568
%\end{tabular}
%\\
%{}&{}\\\begin{tabular}{l}
%{\bf Professor Steve Lalley}\\
%Department of Statistics\\
%University of Chicago\\
%5734 S. University Avenue\\
%Chicago, IL 60637-1514\\
%email: \texttt{lalley@galton.uchicago.edu}\\
%phone: (773) 702-9890
%\end{tabular}
%\\
%{}&{}\\

%\begin{tabular}{l}
%{\bf Professor Michael Wichura}\\
%Department of Statistics\\
%University of Chicago\\
%5734 S. University Avenue\\
%Chicago, IL 60637-1514\\
%email: \texttt{wichura@galton.uchicago.edu}\\
%phone: (773) 702-8329
%\end{tabular}
%&
%{}
%\end{tabular}

\end{document}
